\section{Introduction}

\subsection{Revision History}
\begin{tabular}{| l | l | p{10cm} |}
\hline
\textbf{Version} & \textbf{Date} & \textbf{Changes}\\
\hline
1.0-RC1 & 15/01/2017 & First deadline release.\\
\hline
\end{tabular}

\subsection{Purpose and Scope}
TODOOOOOOOOOOOOO


\subsection{List of Definitions and Abbreviations}
\subsubsection{Acronyms, Abbreviations}
\begin{itemize}
    \item ORAA = Onboard Ride Assistant App
    \item PEJ = PowerEnJoy
   % \item PPP = Payment Processor Provider
    \item SBL = Service Business Logic
    \item SPA = Special Parking Area
    \item UDMA = User Device Mobile App
\end{itemize}
\subsubsection{Definitions}
\begin{itemize}
    \item \textbf{Car:} every vehicle, which respects the requirements, that the system allows the users to use.
    \item\textbf{PowerUser:} user who is already registered to the service and is currently logged in.
    \item \textbf{Safe Parking Area:} pre-defined areas (i.e. streets) where a user is allowed to park.
    \item \textbf{Service Business Logic:} software logic of the service the user do not directly interact with.
    \item \textbf{Special Parking Area:} pre-defined areas (i.e. streets) where a user is allowed to park and where the batteries of the Cars can be plugged into the power grid.
    \item \textbf{Total Base Fare:} amount of money that the user pays for the ride duration only. It does not include any discount or penalty for any other specific condition.
    \item \textbf{Total Ride Fare:} amount of money that the user pays. It includes any discount or penalty for any other specific condition satisfied during the ride.
\end{itemize}


\subsection{List of Reference Documents}
\begin{itemize}
    \item Project’s Assignment document: AA 2016-2017 Software Engineering 2 - Project goal, schedule, and rules.
    \item Software Engineering 2: "PowerEnJoy" Requirements Analysis and Specification Document.
    \item Software Engineering 2: "PowerEnJoy" Design Document.
    \item TOOOOOOOOOOOOOOOOLLLLLLLSSSSSSSSS
\end{itemize}