\section{Introduction}
\subsection{Purpose}
This document is intended for an audience of both system developers and stakeholders. It contains the description of all the requirements the customer asked to be covered by the implementation, all the constraints the system has to deal with, and a variety of scenarios describing system interactions and features.
\subsection{Scope}
This document contains a description of what the digital management system has to implement in order to support an electric-only car-sharing service called PowerEnJoy, providing all basic car-sharing services plus some additional special pricing policies.
\subsection{Definitions, Acronyms, Abbreviations:}
\subsubsection{Acronyms and Abbreviations}
\begin{itemize}
\item GPS = Global Positioning System
\item PEJ = PowerEnJoy
\item PPP = Payment Processor Provider
\item PU = PowerUser
\item SBL = Service Business Logic
\end{itemize}
\subsubsection{Definitions}
\begin{itemize}
\item \textbf{Car:} every vehicle, which respects the requirements, that the system allows the users to use.
\item \textbf{Current Fare:} amount of money that the user would pay if the ride ended in that moment. It does not include any discount or penalty for any other specific condition.
\item \textbf{PowerEnJoy:} name of the service for which the management software to be developed is described in this document; we are going to use this name from now on referring to the software application itself instead of the service. Also referred to from now on as "system" or "platform".
\item \textbf{PowerUser:} user who is already registered to the service and is currently logged in.
\item \textbf{Safe Parking Area:} pre-defined areas (i.e. streets) where a user is allowed to park.
\item \textbf{Service Business Logic:} software logic of the service the user do not directly interact with. 
\item \textbf{Special Parking Area:}  pre-defined areas (i.e. streets) where a user is allowed to park and where the batteries of the Cars can be plugged into the power grid.
\item \textbf{Total Base Fare:} amount of money that the user pays for the ride duration only. It does not include any discount or penalty for any other specific condition.
\item \textbf{Total Ride Fare:} amount of money that the user pays. It includes any discount or penalty for any other specific condition satisfied during the ride.
\item \textbf{Visitor:} user who is not logged in the system.
\end{itemize}
\subsection{Reference}
\begin{itemize}
\item Project's Assignment document: AA 2016-2017 Software Engineering 2 - Project goal, schedule, and rules.
\item IEEE Std 830-1998, IEEE Recommended Practice for Software Requirements Specifications.
\item UML Use case diagram PDF from the course "Sistemi Informativi" of Politecnico of Milan.
\end{itemize}
\subsection{Overview}
This document is split in 4 part:
\begin{itemize}
\item \textbf{Overall Description:} contains general information about the features of the system, constraints, assumptions. 
\item \textbf{Scenarios:} contains an informal description of relevant or typical system usage scenarios.
\item \textbf{Specific Requirements:} contains the detailed descriptions of all the interfaces and requirements to guarantee goals coverage, including relative domain properties. 
\item \textbf{Appendix:} contains the UML class diagram of the system and Alloy models of relevant world entities.
\end{itemize}