\section{Scenarios}

\subsection{Scenario 1: Typical usage situation}
Al is a student and he have to go to University, however public transport is on strike, so he decides to rent a car.  He installs the PowerEnJoy app on his mobile phone, he opens it and look for a nearby Car on the map. He find one at 200 meters from his home. At this point he decides to register to the PEJ service fulfilling all camps with his name, surname, driver licence, email and credit card information. A mail with the password arrives within a minute, he logs in as a PowerUser, and he reserves the previously seen Car. In 20 minutes he is near the car. He opens the app to confirm his proximity to the vehicle, the system let him ask the unlocking of the Car and so that Al can enter, insert his destination on the screen of the Car, start the engine and drive towards his destination. Once arrived he stops, turns off the car and the total amount of the charge displayed on the Car screen will be deducted from his credit car. The Car will lock automatically after one minute. 

\subsection{Scenario 2: No Car available}
John has just left a party, his only wish is to get home as soon as possible but unfortunately he finds out that his car does not start. Looking around he sees a Car with the PowerEnJoy logo on the side. He googles it and find a way to install the PowerEnJoy app. After opening it, he starts looking for that Car in order to reserve it, however he discovers that it is not shown on the map, so it can't be rented. At that point he gives up and falls back to the night service of the local public transport.
% [2] HA SENSO UN CASO IN CUI NON USIAMO IL SISTEMA?
% [re:2] L: it should make sense, as long as we're actually describing user interaction and relative system behavior

\subsection{Scenario 3: Car pooling discount}
Jack is an architect, and he is expected to attend a meeting located in the other side of the city. The day before he finds out that due to the high pollution level his old car is not authorized to be used. Since he need to carry a lot of big papers with him, he does not want to use the public transport. He decided to rent a car using the PowerEnJoy service. Furthermore he proposes to a neighbour to share the ride, so since both Jack, his wife and his colleague need to reach the same destination they are eligible for a discount. The following day Jack launches the PowerEnJoy app, selects the closest Car and, with both his wife and his neighbour, reaches his destination. The system applies a discount since there were at least three people from the start of the journey up to the final destination. When Jack parks the Car he can read the charge of his ride with the discount already applied.
%QUINDI LO SCHERMO DELL'AUTO DEVE MOSTRARE IL PREZZO SCONTATO?
%Lo stesso vale per lo scenario 4

\subsection{Scenario 4: Charged ($\geq$50\%) battery discount}
Elizabeth is attending the local gym, she doesn't live too far from it, but she is not comfortable walking alone in the evening. So she decides to take advantage of the PowerEnJoy service, since there is a Special Parking Area few meters from her home where she can book a fully charged Car. Once arrived to the gym and stopped the Car, she finds out that she consumes far less than half of the battery, indeed on the Car's screen is shown the charge with the discount she is eligible for already applied. %//This way she manage to consume far less the half of the battery and is eligible for a discount. 
%DETTAGLIARE MODALITA(non vanno le accentate...) FUNZIONAMENTO DISCOUNT

\subsection{Scenario 5: Money saving option}
Victor is an hard worker, he has just moved from another city and he hasn't bought a car yet since he need to save as much money as possible. He has just discovered the existence of the PowerEnJoy service and its Money Saving option. He downloads the app, launches it, completes the registration and reserves a near Car. Jack gets in the Car before his reservation expires and inserts his destination on the screen of the Car. He enables the Money Saving option and the navigator shows the Special Parking Areas where he have to park to get a discount. Jack considers that solution suitable for his needs, so he starts his ride. The navigator drives him to the Special Parking Area, John parks the Car and exits it. Within the prescribed time limit he plugs the Car to the power grid, in this way the discount is applied.

\subsection{Scenario 6: Reservation cancelled}
Elena is working as babysitter looking after the son of her friends. She typically left her friends' house when the child's parents are back, and since they uses to be very punctual people she has already reserved a Car using the PoweEnJoy app. Unfortunately, due to a traffic jam, they are late, so she opens the PowerEnjoy app and cancels her reservation.

\subsection{Scenario 7: 1$\euro$ fee}
Nathan and Samuel are two brothers. They reserved a Car in order to go to the cinema. They are leaving home when a water pipe breaks and starts pouring water everywhere in the kitchen. They immediately close the water, but since there is water everywhere they decide to stay home and clean up the wet floor. They forget their reservation, so after the established hour the system deducts the 1$\euro$ penalty.